Indirect elicitation as a necessary condition for consistent surrogate losses

### 2020-06-03 neurips-20/cvx-flats.tex
tweak

An important caveat to the above definitions is that we have required $\Gamma = \prop{L}$ to be nonempty everywhere, meaning that $\exploss{L}{\cdot}{p}$ always achieves a minimum.
\raft{Let's make sure we agree with this paragraph}
While this condition is restrictive, and rules out several popular surrogates such as logistic and exponential loss for binary classification, these are easily rectified for example by thresholding the loss $L'(u,y) = \max(L(u,y),\epsilon)$ for sufficiently small $\epsilon>0$.
The results in this paper are not heavily impacted by this restriction, as for example assuming $\Gamma(p) \neq \emptyset$ whenever $p\in\relint\simplex$ is strong enough to include the above examples without impacting Theorems~\ref{thm:cvx-flats} and~\ref{thm:bayes-risk-lower-bound}.
\raft{In particular, I'm torn about whether this statement is accurate; in the sense that we can restrict to $\P\subseteq\simplex$ I think it's fair, but in the sense that calibration does not imply indirect elicitation without it, probably not}
We expect that a generalization of property elicitation which allows for ``infinite'' predictions (e.g., along a prescribed ray), thereby ensuring a minimum is always achieved for convex losses, would allow us to lift this restriction entirely.
\btw{Some refs / related work commented out here.  I think not as relevant as elicitation complexity.}

>>>>

An important caveat to the above definitions is that we have required $\Gamma = \prop{L}$ to be nonempty everywhere, meaning that $\exploss{L}{\cdot}{p}$ always achieves a minimum.
\raft{Let's make sure we agree with this paragraph}
While this condition is restrictive, and rules out several popular surrogates such as logistic and exponential loss for binary classification, these are easily rectified for example by thresholding the loss $L'(u,y) = \max(L(u,y),\epsilon)$ for sufficiently small $\epsilon>0$.
The results in this paper are not heavily impacted by this restriction, as for example assuming $\Gamma(p) \neq \emptyset$ whenever $p\in\relint\simplex$ is strong enough to include the above examples without impacting Theorems~\ref{thm:cvx-flats} and~\ref{thm:bayes-risk-lower-bound}.
\raft{In particular, I'm torn about whether this statement is accurate; in the sense that we can restrict to $\P\subseteq\simplex$ I think it's fair, but in the sense that calibration does not imply indirect elicitation without it, perhaps not.}
We expect that a generalization of property elicitation which allows for ``infinite'' predictions (e.g., along a prescribed ray), thereby ensuring a minimum is always achieved for convex losses, would allow us to lift this restriction entirely.
\btw{Some refs / related work commented out here.  I think not as relevant as elicitation complexity.}
